countries & logical columns: dev'ed countries

### 2022-11-14 r-report/countries_deved.Rmd
countries fix

---
title: "countries & logical columns: ADP region"
output: pdf_document
date: "2022-10-24"
---

@@

data_base %>%
  filter(region_ar6_6 == "Asia and developing Pacific") %>%
  distinct(country,ISO,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>%
  kable("latex",booktabs = T, longtable = T)
```

>>>>

---
title: "countries & logical columns: dev'ed countries"
output: pdf_document
date: "2022-10-24"
---

@@

data_base %>%
  filter(deved) %>%
  distinct(country,ISO,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>%
  kable("latex",booktabs = T, longtable = T)
```
